### 2019-10-16 thesis/txt/0-introduction.tex
ie -> ir

%There are many different extraction techniques use for this task. Beller et al.  used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI~\cite{beller2017oops}, while Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}. Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}. \bp{anecdotal: keyword search?}. Apart from those there are various more extraction techniques like searching for keywords, ... \todo{more?} \bp{introduce problem: which one to choose}

@@

There are many different extraction techniques used for this task. Beller et al. used regular expressions when analyzing the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}. Such regular expressions are developed by looking at a few exemplary build logs and maintaining them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

Currently we only have anecdotal evidence on the performance of these techniques and when to use which. Developers and researches have little support while choosing which one to use for an extraction task. Our goal for this thesis is to investigate different information extraction techniques and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize the different extraction techniques and answer what influences the suitability of a technique.
We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this extractions and a categorization of the extractions according to their structural position within the log.

We aim to answer the following research questions:
\begin{itemize}
  \item[\textbf{RQ1:}] What criteria influence the suitability of an information extraction technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the extractions of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for extraction tasks requiring a high precision, ... . Extracting information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the extractable information in CI build logs
  \item A model to characterize information extraction techniques from CI build logs
  \item A model to characterize use case scenarios for information extraction from CI build logs
  \item A tool unifying several information extraction techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the extractions according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information extraction techniques \todo{describe \emph{what} we look for with this evaluation}
  \item A extendable scheme supporting decision on (our three) information extraction techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information extraction and retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} present our models for information extraction techniques, use case scenarios for such techniques and extractable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information extraction techniques and the usage of our unified information extraction tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

>>>>

%There are many different retrieval techniques use for this task. Beller et al.  used regular expressions when analysing the failure reasons of ruby and Java Maven buildlogs from TravisCI~\cite{beller2017oops}, while Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}. Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}. \bp{anecdotal: keyword search?}. Apart from those there are various more retrieval techniques like searching for keywords, ... \todo{more?} \bp{introduce problem: which one to choose}

@@

There are many different retrieval techniques used for this task. Beller et al. used regular expressions when analyzing the failure reasons of Ruby and Java Maven build logs from TravisCI~\cite{beller2017oops}. Such regular expressions are developed by looking at a few exemplary build logs and maintaining them whenever new cases are introduced is a tedious and error-prone task~\cite{michael2019regexes}.
Vassallo et al. wrote a custom parser for Java Maven build logs to gather information for build repair hints~\cite{vassallo2018un-break}.
Recently Amar et al. greatly reduced the number of build log lines for a developer to inspect by creating a diff between the logs from a failed and successful build~\cite{amar2019mining}.

Currently we only have anecdotal evidence on the performance of these techniques and when to use which. Developers and researches have little support while choosing which one to use for an retrieval task. Our goal for this thesis is to investigate different information retrieval techniques and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize the different retrieval techniques and answer what influences the suitability of a technique.
We support our assumption by evaluating three chosen techniques, namely regular expression synthesis by example using the Microsoft PROSE library (referred to as PBE), a common text similarity approach (referred to as TS) and simple keyword search (referred to as SKWS).
Our \emph{Failing Build Logs Data Set} encompasses about 800 log files from 80 repositories, labeled with the log part describing the reason a build failed, keywords to search for this retrievals and a categorization of the retrievals according to their structural position within the log.

We aim to answer the following research questions:
\begin{itemize}
  \item[\textbf{RQ1:}] What criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to extract information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}

\plan{results and conclusions of my work}
Our study of the three techniques on \emph{Failing Build Logs Data Set} shows that PROSE is suitable for retrieval tasks requiring a high precision, ... . Extracting information by using text similarity of examples is suitable when ... . Simple keyword search is suitable ... .

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the extractable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item our implementation of regular expression program synthesis using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and extractable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation, as well as their theoretical foundations.
Chapter \ref{sec:data-set} describes the creation of our \emph{The Failing Build Logs Data Set} collected from failed Travis CI build logs, and the labeling and validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

### 2019-10-16 thesis/txt/1-related-work.tex
ie -> ir

\chapter{Related Work}
\label{sec:rw}
\todo{introduction \& glue text}
This section presents various research works adjecent or foundational for our work. Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation. We differentiate our work from the more common production runtime log analysis and cover different information extraction and retrieval techniques. Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.

@@

\section{Build Log Analysis and Augmentation}
Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs. They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text extraction while also covering a wider array of programming languages.

@@

\section{Information Extraction and Retrieval Techniques}
\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}. For our use case, this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}

@@

\section{Program Synthesis by Example}
\review{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information extraction.
}
\mention{prose theory paper \cite{polozov2015flashmeta:}}
\mention{\cite{rolim2017learning}}

>>>>

\chapter{Related Work}
\label{sec:rw}
\todo{introduction \& glue text}
This section presents various research works adjecent or foundational for our work. Starting with studies about Continuous Integration used in software projects, we move on to past works about build log analysis and their augmentation. We differentiate our work from the more common production runtime log analysis and cover different information retrieval techniques. Lastly this section mentions different Programming by Example resources surrounding Microsoft's work on the PROSE library.

@@

\section{Build Log Analysis and Augmentation}
Vassallo et al.~\cite{vassallo2018un-break} tried to shorten the time it takes developers to understand build logs. They summarized relevant information in Maven build logs and augmented them with links to related stack overflow posts. They observed that highlighting the locality and context of an issue is helpful to programmers. We strive to enable a similar summarization by text retrieval while also covering a wider array of programming languages.
\todo{reference their new paper}

@@

\section{Information retrieval and Retrieval Techniques}
\review{Getting the general topic or conceptual information of a text is a common task in information retrieval from semi-structured text sources. Usually this is done by preprocessing the documents, transforming them to a term-by-document matrix. On the matrix we apply a similarity comparison like for example vector space models to calculate the similarity of the different documents to each other~\cite{panichella2016parameterizing}. For our use case, this could be applied by slicing the build logs into lines or small sections. Then similarity measures are used to compare the overall topics in these subparts to the topic of previously labelled logparts.
Instead of receiving a paragraph which is similar to a given query, our works focus more on obtaining specific pieces of texts through regular expressions.}

@@

\section{Program Synthesis by Example}
\todo{how much can/should we explain here? possibly big parts are already explained in related work: vsa, divied and coquer, witness functions, enumeration and ranking (prose theory paper), flash extract specifics like what functions they have (absolute pos, pre/post regex), rankings specific to ci biulg logs?}
\review{
Le et al.~\cite{le2014flashextract:} developed FlashExtract as part of the \emph{Microsoft Program Synthesis using Examples} (PROSE) framework. It is a tool which synthesizes text extraction programs from semi-structured text based on a few given examples. Users can extract multiple fields and structure them with hierarchy and sequence. FlashExtract eliminates the need for the user to understand the entire structure of the processed document and the effort of developing a suitable extraction program themselves.

We are applying FlashExtract to the domain of build logs, using programming by example to take away the need to tediously develop and maintain regular expressions for information retrieval.
}
\mention{prose theory paper \cite{polozov2015flashmeta:}}
\mention{\cite{rolim2017learning}}

### 2019-10-16 thesis/txt/3-data-set.tex
ie -> ir

\section{Build Failure Reason}
\todo{WHY? one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined extraction   cause that would be simple for PROSE extraction -> better comparability}

\section{Data Model}
For our study, described in Chapter \ref{sec:study}, we want to investigate the extraction capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

\subsection{Example Set}
Our data set is organized in example sets. One example set always contains build log in/output examples from the same software repository or project and for one specific build log information. They are all from one repository because we investigate information extraction techniques which are always configured to the scope of one particular software repository or project.
Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.

\subsection{In / Output Example}
In/output examples (I/O examples) are used to configure two of the information extraction techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity. In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example. The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.

@@

\subsection{Categories}
Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the extraction.
To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
If two extractions are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.

@@

The labeler read or skimmed through build log and copy out the substring describing the reason the build failed. Whitespace or special characters were preserved, as they might be crucial for an information extraction technique to detect the desired.
Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).

\section{Validation}
We vaildated our collected labels in two different ways. We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa. In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our extraction of the log part describing the reason the build failed was correct. In the following we describe the results of those two validation studies.

>>>>

\section{Build Failure Reason}
\todo{WHY? one common information developers and researches might want to extract, intentionally not focus on one structurally clearly defined retrieval   cause that would be simple for PROSE retrieval -> better comparability}

\section{Data Model}
For our study, described in Chapter \ref{sec:study}, we want to investigate the retrieval capabilities of three techniques. Therefore, we need a data set of in/output examples for one \texttt{BuildLogInformation}. Furthermore, Keyword search is not configured by such in/output, but search keywords surrounding the desired output. Finally, this section describes our notion of structural categories, which we use to quantify our assumptions on the needed uniformness of in/output examples.

\subsection{Example Set}
Our data set is organized in example sets. One example set always contains build log in/output examples from the same software repository or project and for one specific build log information. They are all from one repository because we investigate information retrieval techniques which are always configured to the scope of one particular software repository or project.
Each example set has an identifying \emph{save name}, a \emph{build log information} that is desired to be extracted by this configuration, and a list of \emph{in / output examples}.

\subsection{In / Output Example}
In/output examples (I/O examples) are used to configure two of the information retrieval techniques we are evaluating for this thesis, PROSE regular expression program synthesis by example and text similarity. In our data set they always consist of an \emph{input path}, linking to the build log file which is the input for this example. The \emph{output} is a substring of that build log, the textual representation of the targeted build log information within the input build log.

@@

\subsection{Categories}
Our intuition was that the ability of PROSE to be able to successfully learn a regex program depended on the structural uniformity of the provided in/output examples.
The regular expressions need a consistent pattern in the build log string at the borders or around the textual representation of a build log information to match on for the retrieval.
To be able to quantify this intuition in our evaluation we assigned \emph{structural categories} to each of the examples within an example set.
If two retrievals are at the same structural location with the build log, meaning they are surrounded by a similar markings, the fall into the same category.
For most cases, two build failure reason examples which fall into one category are outputted either within the same build step or by the same build step tool.

@@

The labeler read or skimmed through build log and copy out the substring describing the reason the build failed. Whitespace or special characters were preserved, as they might be crucial for an information retrieval technique to detect the desired.
Because we are using xml to save our example sets, we also had to make sure to escape respective special characters (ampersand, less than).

\section{Validation}
We vaildated our collected labels in two different ways. We did a second pass of labeling the build failure reason, keywords and categoies on a subset of the data and compared the results to calculate the inter-rater reliability using cohens kappa. In addition, we sent out a survey to the developers, whose commits triggered the builds within our data set and asked them whether our retrieval of the log part describing the reason the build failed was correct. In the following we describe the results of those two validation studies.

### 2019-10-16 thesis/txt/4-tool.tex
ie -> ir

\chapter{Information Extraction Tool}
\label{sec:implementation}
We implemented prototypes for our three focus information extraction techniques to evaluate them on our collected build logs.
This section will present our unified interface and describe the implementation of each of the techniques.

\begin{figure}[h]
	\centering
	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Our tool unifying different information extraction techniques for build logs}
	\label{fig:tool}
\end{figure}

@@

Specific options:
    -a, --action ACTION              Either run an extraction for a example set ('analyze') or run the whole evaluation of it ('evaluate')
    -t, --technique TECHNIQUE        The technique used for creating the extraction program (pbe, ir, keyword, random)
    -e, --example-set EXAMPLE_SET    The filename of the example set to use
    -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
    -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
    -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
    -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
    -v, --verbose                    Print additional interesting output apart from only the extraction output
    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based extraction
    -r, --regex REGEX                Regex to match on build log file content in regex based extraction

Common options:
    -h, --help                       Show this message
\end{lstlisting}
As we implemented the information extraction techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces. Our unified interface then in turn calls the various different IE techniques over the command line.

We provide two different modes: \emph{analysis} and \emph{evaluation}.
The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting extraction on the console output. The \emph{evaluation} takes an

>>>>

\chapter{Information Retrieval Tool}
\label{sec:implementation}
We implemented prototypes for our three focus information retrieval techniques to evaluate them on our collected build logs.
This section will present our unified interface and describe the implementation of each of the techniques.

\begin{figure}[h]
	\centering
	\includegraphics[page=7, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Our tool unifying different information retrieval techniques for build logs}
	\label{fig:tool}
\end{figure}

@@

Specific options:
    -a, --action ACTION              Either run an retrieval for a example set ('analyze') or run the whole evaluation of it ('evaluate')
    -t, --technique TECHNIQUE        The technique used for creating the retrieval program (pbe, ir, keyword, random)
    -e, --example-set EXAMPLE_SET    The filename of the example set to use
    -p, --path PATH                  The path to the file to be analyzed relative to the 'tool/samples' folder
    -s, --selection SELECTION        The example sequence selection technique to use for evaluation (chronological, random, manual (= like defined in file))
    -l, --learning-step-count COUNT  How many steps with increasing example set size to do during evaluation
    -c, --test-count COUNT           How many test files to evaluate the generated program in each learning step of the evaluation
    -v, --verbose                    Print additional interesting output apart from only the retrieval output
    -k, --keywords X,Y,Z             Keywords too filter lines for during keyword search based retrieval
    -r, --regex REGEX                Regex to match on build log file content in regex based retrieval

Common options:
    -h, --help                       Show this message
\end{lstlisting}
As we implemented the information retrieval techniques in different languages, choosing one that fits the respective technique each time, we decided to abstract over language differences for cli arguments by creating a unified interfaces. Our unified interface then in turn calls the various different IE techniques over the command line.

We provide two different modes: \emph{analysis} and \emph{evaluation}.
The \emph{analysis} takes a path to a file you want to analyze and all the configuration necessary for a specific technique and returns the resulting retrieval on the console output. The \emph{evaluation} takes an

### 2019-10-16 thesis/txt/5-study.tex
writing on models chapter, putting pictures into figures, update label names
[wip] toc corrections
ie -> ir

\chapter{Technique Comparison Study}
\label{evaluation}
running evaluation to compare the different techniques

\section{Study Design}
\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
\todo{run!}

@@

\section{Study Results}
\todo{accuracy (or so) of extractions with growing example number // overall averages \& detailed look on special cases //}

\section{Resulting Recommending Scheme}
\todo{draw decision tree}

interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques

>>>>

\chapter{Technique Comparison Study}
\label{sec:study}
\section{Introduction}
running evaluation to compare the different techniques

\section{Method}
\begin{figure}[h]
	\centering
	\includegraphics[page=6, width=\textwidth, trim={0.5cm 0.5cm 0.5cm 0.5cm}, clip]{img/flow-of-research.pdf}
	\caption{Process of our technique comparison study}
	\label{fig:study}
\end{figure}
\todo{run!}

@@

\section{Results}
\todo{accuracy (or so) of retrievals with growing example number // overall averages \& detailed look on special cases //}

\section{Discussion}
\todo{draw decision tree}

interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
\section{Threats to Validity}
